CLT Results

### 2022-04-25 analysis/clt_gafo_merge.Rmd
add new data

ggplot(p1,aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y ="")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("#85AD00"))+
  xlim(-0.2, 0.5)+
  theme_minimal()
```

>>>>

ggplot(p1,aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 stat_halfeye(alpha = .7, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y ="")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00"))+
  xlim(-0.2, 0.5)+
  theme_minimal()
```

### 2022-04-25 analysis/clt_irt_analysis.Rmd
add new data

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 2000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 2000))
firt_3F <- mirt(firt_dat, 3, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 2000))

>>>>

firt_1F <- mirt(firt_dat, 1, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_2F <- mirt(firt_dat, 2, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
firt_3F <- mirt(firt_dat, 3, itemtype = "2PL",  guess = .25,technical = list(NCYCLES = 1000))
